Process RNA-Seq and Genotype Data for TWAS

### 2019-10-08 code/ProcessData.Rmd
Fix Process

>>>>

Diag_Resid_train <- Diag_Resid_train[ (Diag_Resid_train$Chr %in% c(1:22)) == T, ]
Norm_Resid_train <- Norm_Resid_train[ (Norm_Resid_train$Chr %in% c(1:22)) == T, ]

ROS_Diag_Resid_train <- ROS_Diag_Resid_train[ (ROS_Diag_Resid_train$Chr %in% c(1:22)) == T, ]
ROS_Norm_Resid_train <- ROS_Norm_Resid_train[ (ROS_Norm_Resid_train$Chr %in% c(1:22)) == T, ]

colnames(Diag_Resid_train) <- c( colnames(Diag_Resid_train[1:4]), do.call( rbind, strsplit( colnames(Diag_Resid_train[ 5:length(colnames(Diag_Resid_train)) ]), "_") )[,2] )

colnames(Norm_Resid_train) <- c( colnames(Norm_Resid_train[1:4]), do.call( rbind, strsplit( colnames(Norm_Resid_train[ 5:length(colnames(Norm_Resid_train)) ]), "_") )[,2] )

colnames(ROS_Diag_Resid_train) <- c( colnames(ROS_Diag_Resid_train[1:4]), do.call( rbind, strsplit( colnames(ROS_Diag_Resid_train[ 5:length(colnames(ROS_Diag_Resid_train)) ]), "_") )[,2] )

colnames(ROS_Norm_Resid_train) <- c( colnames(ROS_Norm_Resid_train[1:4]), do.call( rbind, strsplit( colnames(ROS_Norm_Resid_train[ 5:length(colnames(ROS_Norm_Resid_train)) ]), "_") )[,2] )
